\thetitle

### 2020-07-08 writing/rational.tex
more tex-os

In contrast to erasure, transient does come with blame. As we discuss in
section~\ref{sec:landscape} though, distinctly from natural blame,
transient may blame more than one components. This peculiarity of 
transient raises the question of how the rational programmer should react
when the language produces a blame set. Our answer is that the rational
programmer has least two reasonable options.  The first option is the rational programmer types
all blamed components at once.  In the second option, the rational
programmer selects the component that is added to the blame set first and types
only that --- after all the types of this first component should be able
to  detect an impedance mismatch earlier in the evaluation of a program. 
As before, the two modes give rise to two different notions of trail:
\begin{quote}
\it 
A  transient all blame trail
is a sequence of configurations $\conf_0,...\conf_n$ of a program
$\system$ where for all $0 \leq i \leq n - 1$, $\conf_i \subset \conf_{i+1}$ and
~$\conf_{i+1} \setminus \conf_i = \mblame{\system, \conf_i}$
where $\mblame{\system, \conf}$ denotes the set of components that $\conf$
blames under transient semantics; 
\end{quote}
\noindent
and
\begin{quote}
\it 
A transient firstborn blame trail
is a sequence of configurations $\conf_0,...\conf_n$ of a program
$\system$ where for all $0 \leq i \leq n - 1$, $\conf_i \subset \conf_{i+1}$ and
  $\conf_{i+1} \setminus \conf_i = \first{\mblame{\system, \conf_i}}$
  where $\first{\mblame{\system, \conf}}$ denotes the first component 
  the transient semantics add to the blame set for $\conf$.
\end{quote}
\noindent As for natural we use the transient all blame trails and 
transient firstborn  trails to define when  transient all blame and 
transient firstborn add value to transient over exceptions and pure
chance.

>>>>

In contrast to erasure, transient does come with blame. As we discuss in
section~\ref{sec:landscape} though, distinctly from natural blame,
transient may blame more than one components. This peculiarity of 
transient raises the question of how the rational programmer should react
when the language produces a blame set. Our answer is that the rational
programmer has least two reasonable options.  The first option is the rational programmer types
all blamed components at once.  In the second option, the rational
programmer selects the component that is added to the blame set first and types
only that --- after all the types of this first component should be able
to  detect an impedance mismatch earlier in the evaluation of a program. 
As before, the two modes give rise to two different notions of trail:
\begin{quote}
\it 
A  transient all blame trail
is a sequence of configurations $\conf_0,...\conf_n$ of a program
$\system$ where for all $0 \leq i \leq n - 1$, $\conf_i \subset \conf_{i+1}$ and
~$\conf_{i+1} \setminus \conf_i = \mblame{\system, \conf_i}$
where $\mblame{\system, \conf}$ denotes the set of components that $\conf$
blames under transient semantics; 
\end{quote}
\noindent
and
\begin{quote}
\it 
A transient firstborn blame trail
is a sequence of configurations $\conf_0,...\conf_n$ of a program
$\system$ where for all $0 \leq i \leq n - 1$, $\conf_i \subset \conf_{i+1}$ and
  $\conf_{i+1} \setminus \conf_i = \first{\mblame{\system, \conf_i}}$
  where $\first{\mblame{\system, \conf}}$ is the first component 
  the transient semantics add to the blame set for $\conf$.
\end{quote}
\noindent As for natural we use the transient all blame trails and 
transient firstborn  trails to define when  transient all blame and 
transient firstborn add value to transient over exceptions and pure
chance.

### 2020-07-08 writing/sample.tex
more tex-os

As we mention above we treat each definitions as a component. A
consequence of this decision is that examining the whole lattice
for each of the mutants becomes unfeasible.
As figure~\ref{table:benchmarks} shows,  most of the programs contain dozens of definitions  
resulting in lattices with as many as $1.41 \times 10^{28}$ configurations.
Since running a single configuration can take 10 minutes or more 
(due to contract checking and instrumentation), running every possible configuration is impractical.
Evidence from similar contexts suggests that randomly sampling the lattice instead of
an exhaustive exploration is an effective alternative~\cite{greenman2019evaluate}.
Hence we randomly sample enough significant configurations
from the lattice to obtain a confidence of 0.95 (with margin of error
0.05) about whether our hypotheses hold or not.
See accompanying appendix for the details of the calculations for the
sufficient size of samples for this estimate.
Exploring more of the lattice would yield higher confidence in the generalizability
of our results for each benchmark in cases where no violations of a property
(e.g. Blame Trail) are found.
In such cases, we could be more certain that we did not simply miss
the configuration(s) that reveal the violation by exploring the lattice more fully.
Our choice of random sample counts reflects the (informal) standard practice of estimating
results to 95 percent or higher confidence.

>>>>

As we mention above we treat each definitions as a component. A
consequence of this decision is that examining the whole lattice
for each of the mutants becomes unfeasible.
As figure~\ref{table:benchmark-descriptions} shows,  most of the programs contain dozens of definitions  
resulting in lattices with as many as $1.41 \times 10^{28}$ configurations.
Since running a single configuration can take 10 minutes or more 
(due to contract checking and instrumentation), running every possible configuration is impractical.
Evidence from similar contexts suggests that randomly sampling the lattice instead of
an exhaustive exploration is an effective alternative~\cite{gtnffvf-jfp-2019}.
Hence we randomly sample enough significant configurations
from the lattice to obtain a confidence of 0.95 (with margin of error
0.05) about whether our hypotheses hold or not.
See accompanying appendix for the details of the calculations for the
sufficient size of samples for this estimate.
Exploring more of the lattice would yield higher confidence in the generalizability
of our results for each benchmark in cases where no violations of a property
(e.g. Blame Trail) are found.
In such cases, we could be more certain that we did not simply miss
the configuration(s) that reveal the violation by exploring the lattice more fully.
Our choice of random sample counts reflects the (informal) standard practice of estimating
results to 95 percent or higher confidence.
